A Streaming Algorithm for 2-Center with Outliers in High Dimensions

### 2015-05-03 paper.tex
Minor Correction about Query Description

Our query algorithm is presented in \Cref{alg:query}.
The idea behind the algorithm is as follows.
By our initial assumption about $p_1$ and by invariants (c), 
we know that $B_1$ completely contains $B_1^*$.
%because $B_1 \cap B_2^* = \emptyset$ . 
But for $B_2$, it might be the case that our assumption about $c_2$ 
was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
To overcome this issue, we try all possible candidates for $c_2$,
and compute, for each possible combinations of 
$B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
using the \textproc{MinCover} function presented in \Cref{alg:compute-min}.

>>>>

Our query algorithm is presented in \Cref{alg:query}.
The idea behind the algorithm is as follows.
By our initial assumption about $p_1$ and  by invariants (c) and (d), if $c_p \in B_2^*$ 
we know that $B_1$ (resp., $B_2$) completely contains $B_1^*$  (resp., $B_2^*$).
%because $B_1 \cap B_2^* = \emptyset$ . 
But it might be the case that our assumption about $c_p$ 
was incorrect, and therefore, $B_1$ (resp., $B_2$) may not completely contain $B_1^*$ (resp., $B_2^*$). 
To overcome this issue, we try all possible candidates for $c_2$,
and compute, for each possible combinations of 
$B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
using the \textproc{MinCover} function presented in \Cref{alg:compute-min}.
